My title

### 2023-03-14 outputs/paper/paper.qmd
data cleaning and graph generation for sex and race

```{r}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8) 
# loading in relevant libraries
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
### Input data ###
income_race<-read.csv(here::here("outputs/data/race_income_data.csv"))

ggplot(subset_data_freq, aes(x = income, y = freq, fill = race)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_x_discrete(labels = c("LT $1000","", "$1000 TO 2999","", "$3000 TO 3999","",
                              "$4000 TO 4999","", "$5000 TO 5999","","$6000 TO 6999", "",
                              "$7000 TO 7999","","$8000 TO 9999","","$10000 - 14999","",
                              "$15000 - 19999","","$20000 - 24999","","$25000 OR MORE")) +
  labs(y = "Numbers of people", title = "Numbers of people of Income by race") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))

@@

```{r}

>>>>

```{r}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8) 
# loading in relevant libraries
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
### Input data ###
income_race<-read.csv(here::here("outputs/data/race_income.csv"))
income_sex<-read.csv(here::here("outputs/data/sex_income.csv"))
```

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Race"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")
income_race$income <- 
  factor(income_race$income, 
         levels = income_label)

#generate graph#
ggplot(income_race, aes(x = income, y = the_number_of_people, fill = race)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "Income level", y = "Numbers of people", title = "U.S. Income Distribution by Race") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8))

@@

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Sex"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")
income_sex$income <- 
  factor(income_sex$income, 
         levels = income_label)

#generate graph#
ggplot(income_sex, aes(x = income, y = the_number_of_people, fill = sex)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "Income level", y = "Numbers of people", title = "U.S. Income Distribution by Sex") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8))
